---
title: "waveST Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette01}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
Name: Zhuoyan Xu

Email: zhuoyan.xu@wisc.edu

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(knitr)
opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  dpi = 200,
  fig.align = "center",
  out.width = 650,
  fig.height = 8,
  fig.width = 8
  )
```

```{r setup, message=FALSE}
if (!require("waveST")) {      
  install.packages("waveST")   
  stopifnot(require("waveST"))
}
if (!require("tidyverse")) {      
  install.packages("tidyverse")   
  stopifnot(require("tidyverse"))
}
if (!require("fields")) {      
  install.packages("fields")   
  stopifnot(require("fields"))
}
theme_set(theme_minimal())


```



# Part 1: Basic Example of running 
```{r, message=FALSE, fig.width= 11, fig.height=8}
waveST = waveST(data = raws[,1:5])

waveST = decompose(waveST, "raw", "SVD", K = 5)
plot(waveST, k = 1, wave = FALSE)


waveST = decompose(waveST, "wave", "SVD", K = 5, tau = 40)
plot(waveST, k = 1, wave = TRUE)
```


# Part 2: Simulation
## Step 1: Data Generation
```{r}
##########==================  Data Generation
NUM_GENES = 300
K = 9

##== Step 1. generate coordinate matrix image with different patterns
# @N_dup, generate duplicates of each matrix pattern with a little permutation 

CMls = generateCoorM(1)
```


We show all the generated pattern:
```{r, fig.width= 8, fig.height=8, result = "hide"}
# show in scaled version
lay = layout(matrix(1:9,3,3,byrow = TRUE))
CMls %>%
  map(~.x/sqrt(sum(.x^2))) %>%
  map(~image.plot(.x, asp = 1))
layout(1)
```

We treat previous 9 patterns as factor genes, i.e. we have 8 factors matrix F = D^2xK (1024x8), where 1024 comes from (D^2) 32^2. We consider p = 500 genes in this simulation generate nxp(1024x500) data matrix by F%*%V, where V is \code{K}xp (8x500), compute the magnitude of each image matrix

```{r}
scales = CMls %>% 
  map_dbl(~sqrt(sum(.x^2)))
## rescale each image matrix to norm 1 (eigen gene has norm 1)
FctGenes = CMls %>% 
  map(~.x/sqrt(sum(.x^2))) %>%
  map_dfc(~as.vector(.)) %>% 
  as.matrix()

LoadGenes = rep(1000,9) %>%
  map_dfc(~.x*rnorm(NUM_GENES)) %>%
  as.matrix(.) %>%
  t(.)

truth = FctGenes %*% LoadGenes

## we generate data by add random noise
raws = truth + matrix(rnorm(prod(dim(truth)), mean = 0, sd = 190), nrow = dim(truth)[1], ncol = dim(truth)[2])

waveST = waveST(data = raws %>% as.tibble())
```

## Step 2: Construct class and apply SVD with or without wavelet.
Without wavelet:
```{r, fig.width= 11, fig.height=8}
waveST = decompose(waveST, "raw", "SVD", K = 5)
plot(waveST, k = 1, wave = FALSE)
```

With wavelet:
```{r, fig.width= 11, fig.height=8}
waveST = decompose(waveST, "wave", "SVD", K = 5, tau = 40)
plot(waveST, k = 1, wave = TRUE)
```






# Part 2: Real Data
## Step 1: Data Generation by _k_ over _A_ filter.
```{r}
res = kOverA_ST(k = 3,A = 7)
viz = res$viz; df = res$df
```

## Step 2: Construct class and apply SVD with or without wavelet.
Without wavelet:
```{r, fig.width= 11, fig.height=8}
waveST = waveST(data = df[,1:5], spatial = viz)
waveST = decompose(waveST, "raw", "SVD", K = 5)
plot(waveST, k = 1, wave = FALSE)
```

With wavelet:
```{r,  fig.width= 11, fig.height=8}
waveST = decompose(waveST, "wave", "SVD", K = 5, tau = 40)
plot(waveST, k = 1, wave = TRUE)
```



